\begin{frame}<presentation:0>
	\frametitle{Courses - M1}
	
	\begin{itemize}
		\setlength{\itemsep}{5pt}
	\item Theoretical Chemistry: Statistical Mechanics applied to Chemistry \\ (Damien Laage \& Guilluam Stirnemann) \hfill \textbf{16.00}/20.
	\item Bio-Inorganic Chemistry (Clotilde Policar) \hfill \textbf{15.90}/20.
	%\item Inorganic Materials (Gilles Wallez) \hfill \textbf{15.25}/20.
	\item Biophysical Chemistry of the Living Matter (Ludovic Jullien) \hfill \textbf{14.00}/20.
	%\item Nuclear Magnetic Resonance (Kong Ooi Tan) \hfill \textbf{14.00}/20. 
	\item Heterogenous Catalysis (Clément Guibert) \hfill \textbf{13.80}/20. \\
	 \hfill et al.

	\item Introduction of QFT (Adel Bilal \& Guilhem Semerjian) \hfill \textbf{13.50}/20.
	\item Introduction of General Relativity (Marios Petropoulos) \hfill \textbf{13.40}/20.
	
	\bigskip

	\item Research Internship M1S2 (Thomas Salez) \hfill \textbf{17.40}/20. \\
	\textit{Brownian Motion near the Soft Surface} \hfill Feb.$\sim$Jul. 2022
	
	\item Research Internship L3S2 (Jérémie Caillat) \hfill \textbf{15.00}/20. \\
	\textit{Simulation of Vibrational ICD on Model Systems with Reduced Dimensions} \\ \hfill Jun.$\sim$Jul. 2020
	\end{itemize}
\end{frame}





\begin{frame}<presentation:0>
	\frametitle{Courses - M2}
	\begin{itemize}
	\setlength{\itemsep}{4pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}
		\item Physics of Fluids and Nonlinear Physics \\ (Arnaud Antkowiak \& Camille Duprat) \hfill \textbf{14.86}/20.
		\item Statistical Field Theory and applications  (Adam Nahum \& Xiangyu Cao) \hfill \textbf{14.44}/20.
		\item Computational and Data-Driven Physics \\ (Alberto Rosso \& Rémi Monasson) \hfill \textbf{13.70}/20.
		\item Soft Matter Physics  (Anke Lindner \& Vincent Démery)  \hfill \textbf{13.00}/20.
		\item Advanced Statistical Physics for soft matter \\ (Christophe Texier \& Jean-Noël Aqua) \hfill \textbf{12.50}/20.
		
		\bigskip \hline
		
		\item Machine Learning (Marc Lelarge) \hfill \textbf{16.00}/20.
		\item Advanced Topics in Markov-chain Monte Carlo (Werner Krauth) \hfill \textbf{15.00}/20.
		\item Statistical Physics 2: Disordered Systems and Interdisciplinary Applications (Francesco Zamponi \& Gregory Schehr)  \hfill \textbf{15.00}/20.
		\item Conformal Field Theory (Benoît Estienne \& Yacine Ikhlef) \hfill \textbf{14.00}/20.
		
		%\\
		
		%\item Research Internship M2S2 (Denis Grebenkov, 18 ECTS) \\ \textit{Probabilistic Approach to Diffusion-mediated Surface Phenomena} \hfill Apr.$\sim$Jul. 2023

		
    \end{itemize}
\end{frame}





\begin{frame}<presentation:0>
	\frametitle{Courses - M2S2}
	\begin{itemize}
		\setlength{\itemsep}{8pt}
		\item Machine Learning (Marc Lelarge) \hfill \textbf{16.00}/20.
		\item Advanced Topics in Markov-chain Monte Carlo \\ (Werner Krauth) \hfill \textbf{15.00}/20.
		\item Statistical Physics 2: Disordered Systems and Interdisciplinary Applications (Francesco Zamponi \& Gregory Schehr)  \hfill \textbf{15.00}/20.
		\item Conformal Field Theory \\ (Benoît Estienne \& Yacine Ikhlef) \hfill \textbf{14.00}/20.
		
		\bigskip
		
		\item Research Internship M2S2 (Denis Grebenkov, 18 ECTS) \\ \textit{Probabilistic Approach to Diffusion-mediated Surface Phenomena} \hfill Apr.$\sim$Jul. 2023
    \end{itemize}
\end{frame}